---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## What is the Most Popular Steak?

I work in a restaurant part-time and I decided to observe and collect data of different orders that been made in the kitchen.

There are four different steaks in our restaurant, this form is used to log what type of steak has been ordered and what sauce the steak goes with, to determine what is the most popular combination in terms of what customers have ordered.

```{r}
library(tidyverse)

## storing csv file into a data frame
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTF7PxEY3OtAhFfY6o17V4Tb7MFWBytX20HV1_DH-saE4clVnPsI9D1PAW8yRrP7U73gtagk3VFLQYa/pub?output=csv")

## creating a new data frame with new variable names
latest_data <- logged_data %>%
  rename(steak_type = 2,
         temperature_cooked = 3,
         sauce_ordered = 4) 
    
## finding the amount of responses and the average temperature
num_respos <- length(latest_data$Timestamp)
average_temperature <- mean(latest_data$temperature_cooked) %>%
  round(1)

## plots of the different variables to compare the differences
steak_plot <- ggplot(data = latest_data) +
  geom_bar(aes(x = steak_type),
           fill = "#FFA500") +
  labs(title = "Steaks Ordered",
       x = "Type of Steak",
       y = "Number of Steaks")
temperature_plot <- ggplot(data = latest_data) +
  geom_bar(aes(y = temperature_cooked),
           fill = "#FF0000") +
  labs(title = "Temperature of Steak",
       x = "Number of Steaks",
       y = "Temperature with 1 = Blue to 6 = Well Done")
sauce_plot <- ggplot(data = latest_data) +
  geom_bar(aes(x = sauce_ordered),
           fill = "#800080") +
  labs(title = "Sauce Ordered With Steak",
       x = "Type of Sauce",
       y = "Number of Sauces")

## presenting all the data
paste("The number of steaks in this data is", num_respos)
print(steak_plot)
print(sauce_plot)
print(temperature_plot)
paste("The mean temperature of the steaks is", average_temperature)

```
